### 2015-02-06 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: update report from WERB comments

\chapter{Fire Incident Summary}
\label{fire_sum}
The account of events for this incident was documented by the Safety Investigation Team of the Prince George's County Fire/EMS Department~\cite{PGCounty2013}. At 21:11 hours on February 24, 2012 Prince George's Fire/EMS Department responded to a structure fire in Riverdale Heights, Maryland with a fire in the basement~\cite{PGCounty2013}. For the purpose of this analysis, the details regarding the timeline are considered to be approximate values. The Prince George's County report~\cite{PGCounty2013} includes narratives of actions of the response personnel. The following narrative of the incident, focused on the events which led to serious burn injuries to two emergency-personnel, was taken from the Prince George's County report~\cite{PGCounty2013}:
\begin{quote}
Truck 809 responded from quarters, as the first due truck company, and arrived on 57th Avenue right behind Engine 807B. When Truck 809 stopped to let Engine 807B layout, Truck 809 Can dismounted the truck and had to walk up the street as it pulled away. Truck 809 Officer observed a lot of smoke moving extremely fast through the front yard and across the street upon exiting the truck. Truck 809 Officer and Truck 809 Forcible Entry proceeded directly to the front door \ldots of the structure. Both of them entered the structure with full PPE, including SCBA, but without the protection of a hose line. Truck 809 Officer and Truck 809 Forcible Entry began primary searches on the first floor. At some point during the primary search, as conditions worsened, the front door closed, trapping Truck 809 Officer and Truck 809 Forcible Entry inside the structure. This situation could not have occurred if a charged hose line was operating inside the structure at the time the door slammed shut. They were the only firefighters operating on the first floor at that time.

@@

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/PGCo_Front} \\ 
\vspace{0.1in}
\includegraphics[width=5in]{../Figures/PGCo_Rear}
\caption{Photographs showing the front (top) and rear (bottom) exterior of the structure after the incident.}
\label{fig:exterior}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_99s}
\input{../Scripts/colorbar_metric_pres} \\
\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_101s}
\input{../Scripts/colorbar_metric_pres}
\caption[Calculated pressure on first floor 1~s before and after front door opens]
{Calculated pressure contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door 0.91~m (3~ft) above the floor.}
\label{fig:pressure_slices}
\end{figure}

@@

The report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were injured after making entry to the first floor and had to either bail out through a window or be rescued through the front door. From Section~\ref{temp}, the conditions on the first floor were initially tenable. After the front door was opened, however, the simulation results indicated that a high hazard area existed in the first floor that exceeded the conditions that would put a firefighter at risk for burn injuries (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{nfpa2013standard}.

@@

\begin{figure}[!ht]
\begin{subfigure}{0.65\textwidth}
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_99s} \\
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_99s} 
\end{subfigure}
\begin{subfigure}{0.35\textwidth}
\input{../Scripts/colorbar_metric_temp}
\input{../Scripts/colorbar_std_temp} \\
\end{subfigure}
\caption[Interior temperature contours 1~s before front door was opened]
{Interior temperature contours 1~s before front door was opened. The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door. The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
\label{fig:int_temp_99s}
\end{figure}

\begin{figure}[!ht]
\begin{subfigure}{0.65\textwidth}
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_101s} \\
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_101s} 
\end{subfigure}
\begin{subfigure}{0.35\textwidth}
\input{../Scripts/colorbar_metric_temp}
\input{../Scripts/colorbar_std_temp} \\
\end{subfigure}
\caption[Interior temperature contours 1~s after front door was opened]
{Interior temperature contours 1~s after front door was opened. The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door. The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
\label{fig:int_temp_101s}
\end{figure}

\begin{figure}[!ht]
\begin{subfigure}{0.65\textwidth}
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_142s} \\
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_142s} 
\end{subfigure}
\begin{subfigure}{0.35\textwidth}
\input{../Scripts/colorbar_metric_temp}
\input{../Scripts/colorbar_std_temp} \\
\end{subfigure}
\caption[Interior temperature contours as firefighters made entry to the structure]
{Interior temperature contours as firefighters made entry to the structure. The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door. The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
\label{fig:int_temp_142s}
\end{figure}

>>>>

\chapter{Fire Incident Summary}
\label{fire_sum}
The account of events for this incident was documented by the Safety Investigation Team of the Prince George's County Fire/EMS Department~\cite{PGCounty2013}. At 21:11 hours on February 24, 2012 Prince George's Fire/EMS Department responded to a structure fire in Riverdale Heights, Maryland with a fire in the basement~\cite{PGCounty2013}. For the purpose of this analysis, the details regarding the timeline are considered to be approximate values. The Prince George's County report~\cite{PGCounty2013} includes narratives of actions of the response personnel. Note that term following the apparatus number (e.g. Truck 809 Can) refers to the seating assignment and operational duties of the firefighters on board. The following narrative of the incident, focused on the events which led to serious burn injuries to two emergency-personnel, was taken from the Prince George's County report~\cite{PGCounty2013}:
\begin{quote}
Truck 809 responded from quarters, as the first due truck company, and arrived on 57th Avenue right behind Engine 807B. When Truck 809 stopped to let Engine 807B layout, Truck 809 Can dismounted the truck and had to walk up the street as it pulled away. Truck 809 Officer observed a lot of smoke moving extremely fast through the front yard and across the street upon exiting the truck. Truck 809 Officer and Truck 809 Forcible Entry proceeded directly to the front door \ldots of the structure. Both of them entered the structure with full PPE, including SCBA, but without the protection of a hose line. Truck 809 Officer and Truck 809 Forcible Entry began primary searches on the first floor. At some point during the primary search, as conditions worsened, the front door closed, trapping Truck 809 Officer and Truck 809 Forcible Entry inside the structure. This situation could not have occurred if a charged hose line was operating inside the structure at the time the door slammed shut. They were the only firefighters operating on the first floor at that time.

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{../Figures/PGCo_Front} \\ 
\vspace{0.1in}
\includegraphics[width=\textwidth]{../Figures/PGCo_Rear}
\caption{Photographs showing the front (top) and rear (bottom) exterior of the structure after the incident.}
\label{fig:exterior}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.8\textwidth]{../Figures/pressure_slice_99s}
\input{../Scripts/colorbar_metric_pres} \\
\vskip10pt
\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.8\textwidth]{../Figures/pressure_slice_101s}
\input{../Scripts/colorbar_metric_pres}
\caption[Calculated pressure on first floor 1~s before and after front door opens]
{Calculated pressure contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door 0.91~m (3~ft) above the floor.}
\label{fig:pressure_slices}
\end{figure}

@@

The report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were seriosuly injured after making entry to the first floor. The interior conditions forced one firefighter to bail out through a window and the other firefighter to be rescued through the front door. From Section~\ref{temp}, the conditions on the first floor were initially tenable. After the front door was opened, however, the simulation results indicated that a high hazard area existed in the first floor that exceeded the conditions that would put a firefighter at risk for burn injuries (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{nfpa2013standard}.

@@

\begin{figure}[!ht]
\begin{subfigure}{0.65\textwidth}
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_99s} \\
\vskip4pt
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_99s} 
\end{subfigure}
\begin{subfigure}{0.35\textwidth}
\input{../Scripts/colorbar_metric_temp}
\input{../Scripts/colorbar_std_temp} \\
\end{subfigure}
\caption[Interior temperature contours 1~s before front door was opened]
{Interior temperature contours 1~s before front door was opened. The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door. The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
\label{fig:int_temp_99s}
\end{figure}

\begin{figure}[!ht]
\begin{subfigure}{0.65\textwidth}
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_101s} \\
\vskip4pt
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_101s} 
\end{subfigure}
\begin{subfigure}{0.35\textwidth}
\input{../Scripts/colorbar_metric_temp}
\input{../Scripts/colorbar_std_temp} \\
\end{subfigure}
\caption[Interior temperature contours 1~s after front door was opened]
{Interior temperature contours 1~s after front door was opened. The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door. The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
\label{fig:int_temp_101s}
\end{figure}

\begin{figure}[!ht]
\begin{subfigure}{0.65\textwidth}
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_142s} \\
\vskip4pt
\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_142s} 
\end{subfigure}
\begin{subfigure}{0.35\textwidth}
\input{../Scripts/colorbar_metric_temp}
\input{../Scripts/colorbar_std_temp} \\
\end{subfigure}
\caption[Interior temperature contours as firefighters made entry to the structure]
{Interior temperature contours as firefighters made entry to the structure. The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door. The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
\label{fig:int_temp_142s}
\end{figure}
